### 2019-11-07 inst/README.rmd
README now contains Rgraphviz install instructions

Once installed, per usual R practice, just load the *Rclean* package with:

>>>>

You will also likely need to install the
[RGraphViz](bioconductor.org/packages/release/bioc/html/Rgraphviz.html):

```{R rgraphviz}

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("Rgraphviz")

Once installed, per usual R practice just load the *Rclean* package
with:
